### 2019-08-22 paper/paper.tex
Added eigenvalue figure to paper.
Added table of optimal values.

\section{Results}
%
We discover four bicycles for four different design speeds (3, 5, 7, and 9 m/s)
that have an optimally low HQM, see Table~\ref{tab:hqm} and satisify all
constraints and parameter boundaries. We belive these bicycles to be physically
realizable with minor differences. The most striking feature is that all of the
bicycle are larger that the reference bicycle in some way.  The 3 m/s bicycle
places both the rider's mass center and the rear frame's mass center close to 3
meters above the ground plane. The 5 and 7 m/s bicycles have wheelbase values
that are simlar to the reference bicycle, but 3 and 9 m/s have very large wheel
bases. The 9 m/s bicycle is very large overall. Only the 5 m/s bicycle is of a
scale close to a typical bicycle. It is noteable that the 9 m/s bicycle has
signficant negative trail.
%
\begin{figure}
  \centering
  \includegraphics[width=6in]{../figures/optimal-geometries.png}
  \caption{Depcitions of the bicycle geometry and geometric representations of
    the inertial quanties for the reference bicycle and four optimal solutions
    at 3, 5, 7, and 9 m/s. Five rigid bodies are shown for each bicycle: front
    wheel (oragne), rear wheel (purple), rear frame (blue), front frame
    (green), and person (red). The solid black lines represent the essential
    bicycle geometry. The dotted black line represents the steer axis. The
    solid colored curves represent the contours of solid ellipsoids with
    equivalent inertia as the principal inertia of the associated rigid body.
    The dotted colored lines represent the extents of the centerial radii of
    gyration of each rigid body.}
\end{figure}
%
\begin{table}
  \caption{Peak HQM values for the reference bicycle and the optimal bicycles
    at each speed.}
  \label{tab:hqm}
  \centering
  \begin{tabular}{llll}
    \toprule
    Speed [m/s] & Reference Peak HQM & Optimal Peak HQM & Percent Improvement \\
    \midrule
    3 & 13.0753 & 2.0118 & 85\% \\
    5 & 4.5213  & 0.0115 & 100\% \\
    7 & 3.0434  & 0.0220 &  99\% \\
    9 & 2.3377  & 0.8386 &  64\% \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\section{Results}
%
We discover four bicycles for four different design speeds (3, 5, 7, and 9 m/s)
that have an optimally low HQM, see Table~\ref{tab:hqm} and satisify all
constraints and parameter boundaries. We belive these bicycles to be physically
realizable with minor differences. The most striking feature is that all of the
bicycle are larger that the reference bicycle in some way.  The 3 m/s bicycle
places both the rider's mass center and the rear frame's mass center close to 3
meters above the ground plane. The 5 and 7 m/s bicycles have wheelbase values
that are simlar to the reference bicycle, but 3 and 9 m/s have very large wheel
bases. The 9 m/s bicycle is very large overall. Only the 5 m/s bicycle is of a
scale close to a typical bicycle. It is noteable that the 9 m/s bicycle has
signficant negative trail.

3
- Rider is over 3 m in the air and leaned forward.
- 3 m wheel base with 0.5 meter positive trail
- wheels are over double the diameter of browser wheels

5 m/s
- rider is laid back a 0.5 meter off ground
- < 1 m wheelbase

7 m/s
- miminal rotatoinal inertia about the steer axis
- tall slender fork/handlebar
- no trail
- half sized wheels (~12 inches)
- normal wheelbase
- rider tipped forward and low (0.6 m)
- vertical steer axis
- 3 m high frame center of mass
\begin{figure}
  \includegraphics[width=6in]{../figures/optimal-geometries.png}
  \caption{Depcitions of the bicycle geometry and geometric representations of
    the inertial quanties for the reference bicycle and four optimal solutions
    at 3, 5, 7, and 9 m/s. Five rigid bodies are shown for each bicycle: front
    wheel (oragne), rear wheel (purple), rear frame (blue), front frame
    (green), and person (red). The solid black lines represent the essential
    bicycle geometry. The dotted black line represents the steer axis. The
    solid colored curves represent the contours of solid ellipsoids with
    equivalent inertia as the principal inertia of the associated rigid body.
    The dotted colored lines represent the extents of the centerial radii of
    gyration of each rigid body.}
\end{figure}
  \caption{Peak HQM values for the reference bicycle and the optimal bicycles
    at each speed.}
  \label{tab:hqm}
    Speed [m/s] & Reference Peak HQM & Optimal Peak HQM & Percent Improvement \\
    3 & 13.0753 & 2.0118 & 85\% \\
    5 & 4.5213  & 0.0115 & 100\% \\
    7 & 3.0434  & 0.0220 &  99\% \\
    9 & 2.3377  & 0.8386 &  64\% \\
\begin{figure}
  \includegraphics[width=6in]{../figures/optimal-eigenvalues.png}
  \caption{}
\end{figure}
  \caption{Optimal principal parameter values for each design speed.}
  \label{tab:optimal-values}
  \begin{tabular}{lllll}
    Parameter & 3 m/s & 5 m/s & 7 m/s & 9 m/s \\
alphaD & 0.66300  & 0.91544    & 1.1228    & 1.076700 \\
alphaH & 0.57150  & -1.2647 &    1.5708    & 0.23760 \\
alphaP & -0.66130 & 1.1497 &     -0.83627  & 1.5584 \\
c      & 0.68780  & -0.0050384 & 0.0010500 & -0.48397 \\
g      & 9.8100   & 9.8100 &     9.8100 &    9.8100 \\
kDaa   & 1.4491   & 1.2179 &     1.3242 &    0.86084 \\
kDbb   & 0.72360  & 1.3868 &     1.2903 &    2.0139 \\
kDyy   & 1.4711   & 1.5585 &     1.5550 &    2.0305 \\
kFaa   & 0.35495  & 0.12585 &    0.063500 &  1.0314 \\
kFbb   & 0.35495  & 0.12585 &    0.063500 &  1.0314 \\
kFyy   & 0.70990  & 0.25170 &    0.12700 &   2.0628 \\
kHaa   & 0.18620  & 0.049106 &   0.0 &       2.8463 \\
kHbb   & 1.2578   & 1.1451 &     2.0055 &    0.16848 \\
kHyy   & 0.63610  & 0.38324 &    0.81835 &   0.66922 \\
kPaa   & 0.36797  & 0.36797 &    0.36797 &   0.36797 \\
kPbb   & 0.15276  & 0.15276 &    0.15276 &   0.15276 \\
kPyy   & 0.36717  & 0.36717 &    0.36717 &   0.36717 \\
kRaa   & 0.47910  & 0.25306 &    0.073095 &  1.5135 \\
kRbb   & 0.47910  & 0.25306 &    0.073095 &  1.5135 \\
kRyy   & 0.95820  & 0.50612 &    0.14619 &   3.0270 \\
lP     & 1.7280   & 1.7280 &     1.7280 &    1.7280 \\
lam    & -0.21250 & 0.27137 &    -0.027560 & 0.23941 \\
mD     & 3.2233   & 11.534 &     10.315 &    7.0223 \\
mF     & 1.6211   & 4.4038 &     2.6441 &    5.5058 \\
mH     & 0.25000  & 0.25000 &    0.49309 &   3.5435 \\
mP     & 83.500   & 83.500 &     83.500 &    83.500 \\
mR     & 12.625   & 8.3601 &     6.3080 &    2.2534 \\
rF     & 0.70990  & 0.25170 &    0.12700 &   2.0628 \\
rR     & 0.95820  & 0.50612 &    0.14619 &   3.0270 \\
v      & 3.0      & 5.0 &        7.0 &       9.0 \\
w      & 2.8655   & 0.84711 &    1.1570 &    5.5573 \\
wP     & 0.48300  & 0.48300 &    0.48300 &   0.48300 \\
xD     & 0.95820  & 0.28749 &    0.42710 &   1.0204 \\
xF     & 2.8655   & 0.84711 &    1.1570 &    5.5573 \\
xH     & 2.3561   & 0.53227 &    1.1449 &    5.6145 \\
xP     & 0.76460  & 0.27642 &    0.52614 &   1.0791 \\
xR     & 0.0      & 0.0 &        0.0 &       0.0 \\
yD     & 0.0      & 0.0 &        0.0 &       0.0 \\
yF     & 0.0      & 0.0 &        0.0 &       0.0 \\
yH     & 0.0      & 0.0 &        0.0 &       0.0 \\
yP     & 0.0      & 0.0 &        0.0 &       0.0 \\
yR     & 0.0      & 0.0 &        0.0 &       0.0 \\
zD     & -2.6050  & -2.7190 &    -2.9764 &   -4.0653 \\
zF     & -0.70990 & -0.25170 &   -0.12700 &  -2.0628 \\
zH     & -1.2977  & -0.78065 &   -1.3399 &   -1.7755 \\
zP     & -3.1937  & -0.45256 &   -0.58632 &  -2.6623 \\
zR     & -0.95820 & -0.50612 &   -0.14619 &  -3.0270 \\
